Guarded Recursion in Agda via Sized Types

### 2019-01-27 code-oneclock-paper/latex/paper.tex
constructor down in Subst and associated equalities
Rewriting
Shortening in definition of const
First version of an abstract

\newunicodechar{⊤}{$\top$}
\newunicodechar{≡}{$\equiv$}
\newunicodechar{₁}{$_1$}
\newunicodechar{₂}{$_2$}
\newunicodechar{₃}{$_3$}
\newunicodechar{Γ}{$\Gamma$}
\newunicodechar{Δ}{$\Delta$}
\newunicodechar{Σ}{$\Sigma$}
\newunicodechar{α}{$\alpha$}
\newunicodechar{β}{$\beta$}
\newunicodechar{η}{$\eta$}
\newunicodechar{γ}{$\gamma$}
\newunicodechar{ε}{$\varepsilon$}
\newunicodechar{θ}{$\theta$}
\newunicodechar{λ}{$\lambda$}
\newunicodechar{μ}{$\mu$}
\newunicodechar{κ}{$\kappa$}
\newunicodechar{π}{$\pi$}
\newunicodechar{∈}{$\in$}
\newunicodechar{⊞}{$\boxplus$}
\newunicodechar{⊠}{$\boxtimes$}
\newunicodechar{∁}{$\mathbb{C}$}
\newunicodechar{►}{$\blacktriangleright$}
\newunicodechar{▻}{$\vartriangleright$}
\newunicodechar{𝟙}{\textbf{1}}
\newunicodechar{∙}{$\cdot$}
\newunicodechar{∀}{$\forall$}
\newunicodechar{ℓ}{$\ell$}
\newunicodechar{∅}{$\varnothing$}
\newunicodechar{⟶}{$\rightarrow$}
\newunicodechar{□}{$\square$}
\newunicodechar{⇡}{$\uparrow$}
\newunicodechar{⊛}{$\circledast$}
\newunicodechar{⊎}{$\uplus$}
\newunicodechar{⟨}{$\langle$}
\newunicodechar{⟩}{$\rangle$}
\newunicodechar{■}{$\blacksquare$}
\newunicodechar{∎}{$\blacksquare$}
\newunicodechar{⇒}{$\Rightarrow$}
\newunicodechar{⊕}{$\oplus$}
\newunicodechar{⊗}{$\otimes$}
\newunicodechar{∼}{$\sim$}
\newunicodechar{≈}{$\approx$}
\newunicodechar{⊔}{$\sqcup$}
\newunicodechar{⟦}{$\llbracket$}
\newunicodechar{⟧}{$\rrbracket$}
\newunicodechar{⊥}{$\bot$}
\newunicodechar{∞}{$\infty$}
\newunicodechar{⇑}{$\Uparrow$}
\newunicodechar{≃}{$\simeq$}
% Add more as you need them (shouldn't happen often).

@@

\begin{abstract}
Lorem ipsum dolor sit amet, consectetur adipiscing elit. Praesent convallis orci arcu, eu mollis dolor. Aliquam eleifend suscipit lacinia. Maecenas quam mi, porta ut lacinia sed, convallis ac dui. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Suspendisse potenti. 
 \end{abstract}

@@

\section{Preliminaries}
\label{sec:prelim}
\input{Prelude/Basics}
%% \input{Presheaves/Presheaves}
%% \input{Presheaves/Const}
%% \input{Presheaves/Terminal}
%% \input{Presheaves/Product}
%% \input{Presheaves/Sum}
%% \input{Presheaves/Exp}
%% \input{CloTT/Structure/Contexts}
%% \input{CloTT/Structure/Types}
%% \input{CloTT/Structure/Terms}
%% \input{CloTT/Structure/DefinitionalEquality}
%% \input{CloTT/Structure/ContextOperations}
%% \input{CloTT/Structure/Subst}
%% \input{CloTT/TypeFormers/UnitType}
%% \input{CloTT/TypeFormers/SumType}
%% \input{CloTT/TypeFormers/ProductType}
%% \input{CloTT/TypeFormers/FunctionType}
%% \input{CloTT/TypeFormers/ClockQuantification}
%% \input{CloTT/TypeFormers/Later}
%% \input{CloTT/TypeFormers/LaterType}
%% \input{CloTT/TypeFormers/WeakenClock}
%% \input{CloTT/TypeFormers/Fix}
%% \input{CloTT/TypeFormers/Force}

@@

\input{Presheaves/Const}

\input{Presheaves/Exp}

\subsection{Modelling Simple Type Theory}
%\label{sec:kripke}
\input{CloTT/Structure/Contexts}

@@

\section{Modelling Guarded Recursion}
\label{sec:guarded}
Now we have the simple type formers and their terms.
The next step is to add the type formers required for guarded recursion.
We start by defining clock quantification and the later modality, and how to construct terms of those types.
In addition, we define the fixpoint combinator.
We end this section by giving a type former for guarded recursive types.

>>>>

\newunicodechar{⊤}{$\top$}
\newunicodechar{≡}{$\equiv$}
\newunicodechar{₁}{$_1$}
\newunicodechar{₂}{$_2$}
\newunicodechar{₃}{$_3$}
\newunicodechar{Γ}{$\Gamma$}
\newunicodechar{Δ}{$\Delta$}
\newunicodechar{Σ}{$\Sigma$}
\newunicodechar{α}{$\alpha$}
\newunicodechar{β}{$\beta$}
\newunicodechar{η}{$\eta$}
\newunicodechar{γ}{$\gamma$}
\newunicodechar{ε}{$\varepsilon$}
\newunicodechar{θ}{$\theta$}
\newunicodechar{λ}{$\lambda$}
\newunicodechar{μ}{$\mu$}
\newunicodechar{κ}{$\kappa$}
\newunicodechar{π}{$\pi$}
\newunicodechar{∈}{$\in$}
\newunicodechar{⊞}{$\boxplus$}
\newunicodechar{⊠}{$\boxtimes$}
\newunicodechar{∁}{$\mathbb{C}$}
\newunicodechar{►}{$\blacktriangleright$}
\newunicodechar{▻}{$\vartriangleright$}
\newunicodechar{𝟙}{\textbf{1}}
\newunicodechar{∙}{$\cdot$}
\newunicodechar{∀}{$\forall$}
\newunicodechar{ℓ}{$\ell$}
\newunicodechar{∅}{$\varnothing$}
\newunicodechar{⟶}{$\rightarrow$}
\newunicodechar{□}{$\square$}
\newunicodechar{⇡}{$\uparrow$}
\newunicodechar{⊛}{$\circledast$}
\newunicodechar{⊎}{$\uplus$}
\newunicodechar{⟨}{$\langle$}
\newunicodechar{⟩}{$\rangle$}
\newunicodechar{■}{$\blacksquare$}
\newunicodechar{∎}{$\blacksquare$}
\newunicodechar{⇒}{$\Rightarrow$}
\newunicodechar{⊕}{$\oplus$}
\newunicodechar{⊗}{$\otimes$}
\newunicodechar{∼}{$\sim$}
\newunicodechar{≈}{$\approx$}
\newunicodechar{⊔}{$\sqcup$}
\newunicodechar{⟦}{$\llbracket$}
\newunicodechar{⟧}{$\rrbracket$}
\newunicodechar{⊥}{$\bot$}
\newunicodechar{∞}{$\infty$}
\newunicodechar{⇑}{$\Uparrow$}
\newunicodechar{≃}{$\simeq$}
\newunicodechar{∘}{$\circ$}
% Add more as you need them (shouldn't happen often).

@@

\begin{abstract}
Coinduction allows programming and reasoning with possibly nonterminating programs and potentially infinite objects.
In this paper, we compare two approaches for extending type theory with coinduction and coinductive types.
More specifically, we show that guarded recursion and guarded recursive types can be simulated with sized types.
We do this by defining a model of guarded recursion in type theory extended with sized types.
The model is variation of the topos of trees, and it is formalized in Agda.
\end{abstract}

@@

\section{The Host Type Theory}
\label{sec:prelim}
\input{Prelude/Basics}
%% \input{Presheaves/Presheaves}
%% \input{Presheaves/Const}
%% \input{Presheaves/Terminal}
%% \input{Presheaves/Product}
%% \input{Presheaves/Sum}
%% \input{Presheaves/Exp}
%% \input{CloTT/Structure/Contexts}
%% \input{CloTT/Structure/Types}
%% \input{CloTT/Structure/Terms}
%% \input{CloTT/Structure/DefinitionalEquality}
%% \input{CloTT/Structure/ContextOperations}
%% \input{CloTT/Structure/Subst}
%% \input{CloTT/TypeFormers/UnitType}
%% \input{CloTT/TypeFormers/SumType}
%% \input{CloTT/TypeFormers/ProductType}
%% \input{CloTT/TypeFormers/FunctionType}
%% \input{CloTT/TypeFormers/ClockQuantification}
%% \input{CloTT/TypeFormers/Later}
%% \input{CloTT/TypeFormers/LaterType}
%% \input{CloTT/TypeFormers/WeakenClock}
%% \input{CloTT/TypeFormers/Fix}
%% \input{CloTT/TypeFormers/Force}

@@

\input{Presheaves/Const}
\input{Presheaves/Exp}

\subsection{Modelling Simple Types}
%\label{sec:kripke}
\input{CloTT/Structure/Contexts}

@@

\section{Modelling Guarded Recursion}
\label{sec:guarded}
Now we have the simple type formers and their terms.
The next step is to add the type formers required for guarded recursion.
We start by defining clock quantification and the later modality, and how to construct terms of those types.
With this in place, we define the fixpoint combinator.
In the end, we give the type former for guarded recursive types.
